Prediction of PIK3CA mutation with gene expression

### 2020-04-08 plosOne/plosOne.Rmd
aupr
figure legend

abstract: |
  Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante cursus gravida non sed sem. Nullam sapien tellus, commodo id velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id. Nunc convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.

@@

```{r}
knitr::read_chunk('../prediction.R')
```

@@

@@

>>>>

abstract: |

@@

@@

The trainset AUROC was 0.93 and the testset AUROC was 0.84. The AUPR of trainset was 0.74 and the testset AUPR was 0.771.

```{r}
load("../result.RData")
```

@@

Figure 1. Summary of modeling results

(A) Left: receiver operating characteristic (ROC) curve right: precision recall (PR) curve of trainset and testset. The horizontal green line is the PIK3CA mutation rate (0.11)  (B) Correlation between trainset and testset of area under receiver operating characteristic curve (AUROC) and area under precision recall curve (AUPR) among cancer type. The abbreviations are explained in S1 appendix. (C) Correlation between the PIK3CA mutation rate of area under receiver operating characteristic curve (AUROC) and area under precision recall curve (AUPR).

Figure 2. Coefficients of model

(A) Top 30 high coefficients of mRNA. (B) Coefficients of cancer types. The abbreviations are explained in S1 appendix.

# Supporting information

S1 Appendix. 
S2 Figure.
S1 Table.  
S2 Table.  
S3 Table.
